---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning=FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# farsutils

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/carolynwhooks/farsutils.svg?branch=main)](https://travis-ci.com/carolynwhooks/farsutils)
[![R-CMD-check](https://github.com/carolynwhooks/farsutils/workflows/R-CMD-check/badge.svg)](https://github.com/carolynwhooks/farsutils/actions)
<!-- badges: end -->

The goal of farsutils is to provide utilities to read, summarize and plot accident data from yearly accident data the Highway Traffic Safety Adminitration Fatality Analysis Reporting System FARS.


## Installation

You can install the development version of farsutils like so:

``` r
install_github("carolynwhooks/farsutils")
```

## Example

This is a basic example which shows you how to solve a common problem:
- Reading in sample data included with the package
```{r example}
suppressPackageStartupMessages(library(farsutils))
## Reading in sample data included with the package
fileName <- system.file("extdata","accident_2013.csv.bz2",package="farsutils")
data2013 <- fars_read(fileName)
head(data2013,2)
```

